% sections/experience.tex
\section{Experience}

\entry{Senior Software Engineer / Architect}{L5E, LLC dba 5}{Irving, TX}{Sep 2019 -- Present}
\begin{itemize}
  \item Led migration of a legacy PHP energy management platform to the Laravel framework,
        improving maintainability and enabling structured feature development.
  \item Established CI/CD pipelines for the Laravel application, automating testing and
        deployment workflows.
  \item Expanded platform infrastructure into AWS using serverless and managed services
        including Python Lambdas, ECS Fargate, S3, and CloudFront.
  \item Integrated AI-assisted development into day-to-day engineering using Claude Code,
        OpenAI Codex, and the Anthropic and OpenAI APIs -- building agentic workflows,
        custom tooling, and LLM-backed features to accelerate delivery across the stack.
\end{itemize}
\vspace{0.6em}

\entry{Software Developer}{DXC Technology}{Plano, TX}{Sep 2015 -- Aug 2019}
\begin{itemize}
  \item Maintained and extended a Symfony-based managed security alerts application through
        corporate transitions from HP to HPE Security to DXC Technology.
  \item Drove modernization of the platform into AWS serverless architecture using Lambda
        functions and Elasticsearch for security event processing and search.
\end{itemize}
\vspace{0.6em}

\entry{Software Developer}{Rocky Mountain Publishing, LLC dba HomeCEU}{Plano, TX}{Oct 2013 -- Jun 2015}
\begin{itemize}
  \item Provided support and feature development for a primary LMS application server.
  \item Worked in a Scrum Agile environment using PHP, MySQL, Bash, and Ruby.
\end{itemize}

\vspace{1em}